---
title: "PREPARE Primary Analysis"
author: "SB"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
  pdf_document:
    toc: TRUE
---

# Data

```{r setup, include=FALSE}
	knitr::opts_chunk$set(echo = FALSE)
	source('PREPAREStat.R');
```

## Raw Data

```{r echo = T}
	paths = resavePrepareData(preparePaths, doSave = FALSE);
	# Patient data
	data = readData(paths$data);
	# Events
	dataE = readEventData(paths$dataE);
	# Genotypes
	dataG = readGenotypes(pathGts = paths$dataG, pathClin = paths$data);
	# PGx Guidelines
	drug2gene = readActionabilityRules(paths$drug2gene);
	# Nurse assemssments
	dataN = readTable(paths$dataN);
```

## Pre-computations

```{r}
 	idsActionable = ComputeActionability(dataG, drug2gene);
	dataFu = dataAnalysisComputeFollowUp(dataN);
	idsFu = dataFu$STUDYCODE[ nif(dataFu$followup >= 3) ]
	idsIncludedBaseline = data$STUDYCODE;
```

# Primary Analysis (gatekeeper 1; actionables)

## Cases/Controls

```{r}
	evsPrimary = eventFunnelFull(dataE, data, dataG, drug2gene, NULL, CodeTrans);
	if (length(evsPrimary$STUDYCODE) != length(unique(evsPrimary$STUDYCODE))) {
		stop('Events not unique');
	}
	idsCases = intersect(evsPrimary$STUDYCODE, idsActionable);
	idsControl = idsControlsFromPosNeg(data, list(idsFu, idsIncludedBaseline, idsActionable), idsCases);
```

## Full data set

```{r}
	dataPrim = dataForCasesControls(data, idsCases, idsControl, 'outcomePrim',
		pathEQ5D = paths$pathEQ5D, pathNaller = paths$pathNaller, pathCOME = paths$pathCOME);
```

## Regression model (gatekeeper 1)

Analyze actionable patients.

### Descriptives

```{r results = 'asis'}
	cat(Kable(Df(sampleTable(dataPrim, 'outcomePrim', 'STUDYARMC'))))
```

### Random effects model

```{r}
	# control arm is reference level
	f1 = outcomePrim ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + (1|COUNTRY:CENTER)
	rPrim = glmer(f1, family = binomial(), data = dataPrim, glmerControl(optimizer = 'bobyqa', boundary.tol = 0, tol = 1e-3, optCtrl = list(maxfun = 1e5)));
	print(summary(rPrim));
```

Regression Table log-odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrim, doExp = F))
```

Regression Table odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrim, doExp = T))
```

# Primary analysis: Gatekeeper 2

Analyze all patients (irrespective of actionability status).

## Cases/Controls

```{r}
	idsCasesG2 = evsPrimary$STUDYCODE;
	idsControlsG2 = idsControlsFromPosNeg(data, list(idsFu, idsIncludedBaseline), idsCasesG2);
```

## Data set

```{r}
	dataG2Prim = dataForCasesControls(data, idsCasesG2, idsControlsG2, 'outcomePrimG2',
		pathEQ5D = paths$pathEQ5D, pathNaller = paths$pathNaller, pathCOME = paths$pathCOME);
```

### Descriptives

```{r results = 'asis'}
	cat(Kable(Df(sampleTable(dataG2Prim, 'outcomePrimG2', 'STUDYARMC'))))
```

Number of patients overlapping with primary analysis

```{r}
	print(length(intersect(dataPrim$STUDYCODE, dataG2Prim$STUDYCODE)))
```

## Random effects model

```{r}
	f1 = outcomePrimG2 ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + (1|COUNTRY:CENTER);
	print(missingness(dataG2Prim, f1))

	rPrimG2 = glmer(f1, family = binomial(), data = dataG2Prim, glmerControl(optimizer = 'bobyqa', boundary.tol = 0, tol = 1e-3, optCtrl = list(maxfun = 1e5)));
	print(summary(rPrimG2));
```

Regression Table log-odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrimG2, doExp = F))
```

Regression Table odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrimG2, doExp = T))
```

# Negative controls

Analyze non-actionable patients.

### Cases/Controls

```{r}
	idsCasesNC = setdiff(evsPrimary$STUDYCODE, idsActionable);
	idsControlsNC0 = idsControlsFromPosNeg(data, list(idsFu, idsIncludedBaseline), idsCasesNC);
	idsControlsNC = setdiff(idsControlsNC0, idsActionable)
```

## Data set

```{r}
	dataNCprim = dataForCasesControls(data, idsCasesNC, idsControlsNC, 'outcomePrimNC',
		pathEQ5D = paths$pathEQ5D, pathNaller = paths$pathNaller, pathCOME = paths$pathCOME);
```

### Descriptives

```{r results = 'asis'}
	cat(Kable(Df(sampleTable(dataNCprim, 'outcomePrimNC', 'STUDYARMC'))))
```

Number of patients overlapping with primary analysis

```{r}
	print(length(intersect(dataPrim$STUDYCODE, dataNCprim$STUDYCODE)))
```


## Random effects model

```{r}
	f1 = outcomePrimNC ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + (1|COUNTRY:CENTER);
	rPrimNC = glmer(f1, family = binomial(), data = dataNCprim, glmerControl(optimizer = 'bobyqa', boundary.tol = 0, tol = 1e-3, optCtrl = list(maxfun = 1e5)));
	print(summary(rPrimNC));
```

Regression Table log-odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrimNC, doExp = F))
```

Regression Table odds

```{r results = 'asis'}
	CatKableDf(coefficientsTable(rPrimNC, doExp = T))
```


# Session info

```{r}
	sessionInfo()
```
