---
title: "PREPARE Negative controls Analysis"
author: "SB, CHvdW"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
  pdf_document:
    toc: TRUE
---

# Description

# Data

```{r setup, include=FALSE}
	knitr::opts_chunk$set(echo = FALSE)
	Library('glmnet');
	source('PREPAREStat.R');
```

Seed
```{r}
	#generateSeed()
	mySeed = 1161383539;
```

```{r echo = T}
	paths = resavePrepareData(preparePaths, doSave = FALSE);
	# Patient data
	data = readData(paths$data);
	# Events
	dataE = readEventData(paths$dataE);
	# Genotypes
	dataG = readGenotypes(pathGts = paths$dataG, pathClin = paths$data);
	# PGx Guidelines
	drug2gene = readActionabilityRules(paths$drug2gene);
	# Nurse assemssments
	dataN = readTable(paths$dataN);
```

```{r echo = T}
 	idsActionable = ComputeActionability(dataG, drug2gene);
	dataFu = dataAnalysisComputeFollowUp(dataN);
	idsFu = dataFu$STUDYCODE[ nif(dataFu$followup >= 3) ]
	#idsIncludedBaseline = data$STUDYCODE[
	#	data$ELIGIBLE == 'Yes' & !nif(as.integer(data$WITHDRAWREASON) == 1) ]
	idsIncludedBaseline = data$STUDYCODE;
```

## Data set Negative controls

```{r echo = T}
	evs2 = eventFunnelFull(dataE, data, dataG, drug2gene, Drugs, CodeTrans);
	idsCasesNC = setdiff(evs2$STUDYCODE, idsActionable);

	idsControlsNC0 = idsControlsFromPosNeg(data, list(idsFu, idsIncludedBaseline), idsCasesNC);
	idsControlsNC = setdiff(idsControlsNC0, idsActionable)
```


```{r}
	dataNCprim = dataForCasesControls(data, idsCasesNC, idsControlsNC, 'outcomePrimNC',
		pathEQ5D = paths$pathEQ5D, pathNaller = paths$pathNaller, pathCOME = paths$pathCOME);
	dataWdrugs = computeDrugColumns(dataNCprim);
	dataNC = dataWdrugsPer = computePeriod(dataWdrugs$data);
```

## Negative controls, case-mix correction using penalized regression

```{r}
	f1 = outcomePrimNC ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + COUNTRY:CENTER + period + STUDYARMC:COUNTRY;
	f1Drugs = formula.add.rhs(f1, paste('COUNTRY*', dataWdrugs$drugs, sep = ''));
	mm = model_matrix_from_formula(f1Drugs, dataNC);
	set.seed(mySeed);
	rDrugPer = cv.glmnet(mm$mm, mm$response, family = 'binomial', nfolds = 20, alpha = .2);
```

All coefficients

```{r results = 'asis'}
	cfs = coefficients(rDrugPer)
	CatKableDf(as.matrix(cfs[!duplicated(row.names(cfs)), , drop = F]))
```

Non-zero coefficients

```{r results = 'asis'}
	cfs = Df_(as.matrix(cfs[!duplicated(row.names(cfs)), , drop = F]));
	CatKableDf(cfs[ cfs[, 1] != 0, , drop = F])
```

### Refit the model

The model is refitted using a standard logistic regression, treating the elastic net model as a model selection step.

```{r}
	# refit
	ns = names(which(coefficients(rDrugPer)[, 1] != 0));
	d0 = Df_(cbind(mm$response, mm$mm[, ns]), min_ = 'X.Intercept.', headerMap = list(V1 = 'outcome'));
	r0 = glm(outcome ~ ., d0, family = 'binomial');
	print(summary(r0))
```

```{r results = 'asis'}
	CatKableDf(coefficients(summary(r0)))
```

```{r results = 'asis'}
	CatKableDf(coefficientsTable(r0, doExp = F))
```

```{r results = 'asis'}
	CatKableDf(coefficientsTable(r0, doExp = T))
```


# Primary analysis, case-mix correction using penalized regression

```{r}
	evsPrimary = eventFunnelFullA(dataE, data, dataG, drug2gene, NULL, CodeTrans);
	if (length(evsPrimary$STUDYCODE) != length(unique(evsPrimary$STUDYCODE))) {
		stop('Events not unique');
	}
	idsCases = evsPrimary$STUDYCODE;
	idsControl = idsControlsFromPosNeg(data, list(idsFu, idsIncludedBaseline, idsActionable), idsCases);
	dataPrim0 = dataForCasesControls(data, idsCases, idsControl, 'outcomePrim',
		pathEQ5D = paths$pathEQ5D, pathNaller = paths$pathNaller, pathCOME = paths$pathCOME);
	dataWdrugs = computeDrugColumns(dataPrim0);
	dataPrim = dataWdrugsPer = computePeriod(dataWdrugs$data);
```

```{r}
	f1Pen = outcomePrim ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + COUNTRY:CENTER + period;
	f1DrugPenalized = formula.add.rhs(f1Pen, paste('COUNTRY*', dataWdrugs$drugs, sep = ''));
	mm = model_matrix_from_formula(f1DrugPenalized, dataPrim);
	set.seed(mySeed + 1);
	#rPrimPen = cv.glmnet(mm$mm, mm$response, family = 'binomial', nfolds = 20, alpha = .2);
	rPrimPen = cv.glmnet(mm$mm, mm$response, family = 'binomial', nfolds = 20, alpha = .25);
```

All coefficients

```{r results = 'asis'}
	cfs = coefficients(rPrimPen)
	CatKableDf(as.matrix(cfs[!duplicated(row.names(cfs)), , drop = F]))
```

Non-zero coefficients

```{r results = 'asis'}
	cfs = Df_(as.matrix(cfs[!duplicated(row.names(cfs)), , drop = F]));
	CatKableDf(cfs[ cfs[, 1] != 0, , drop = F])
```

Refit
```{r}
	ns = names(which(coefficients(rPrimPen)[, 1] != 0));
	d0 = Df_(cbind(mm$response, mm$mm[, ns]), min_ = 'X.Intercept.', headerMap = list(V1 = 'outcome'));
	r0 = glm(outcome ~ ., d0, family = 'binomial');
	print(summary(r0))
```

```{r results = 'asis'}
	CatKableDf(coefficients(summary(r0)))
```

```{r results = 'asis'}
	CatKableDf(coefficientsTable(r0, doExp = F))
```

```{r results = 'asis'}
	CatKableDf(coefficientsTable(r0, doExp = T))
```


# Negative control, case-mix correction using offset

Case-mix is defined by the drug-distributions across centers and across study arms within centers. The case-mix is corrected for by a two-stage process. First, drug-effects are estimated by a stratified analysis. In a logistic model, the intercept of the model characterizes the drug-related probability for a side-effect. This intercept is used as an offset in the ensuing analysis to correct for a drug effect.

```{r}
	f1Red = outcomePrimNC ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY;

	drugEffects = by(dataNCprim, dataNCprim$INDDRUG1, function(d) {
		#print(dim(d));
		N = dim(d)[1];
		rPrimNC = try(glm(f1Red, data = d, family = binomial()), silent = TRUE);
		if (any(class(rPrimNC) == 'try-error')) return(c(N, NA));
		return(c(N, coefficients(summary(rPrimNC))['(Intercept)', 'Estimate']));
	});
	drugEff = do.call(rbind, drugEffects);
	drugEff[is.na(drugEff[, 2]), 2] = 0;
	off = drugEff[which.indeces(dataNCprim$INDDRUG1, row.names(drugEff), ret.na = TRUE), 2];
	off[is.na(off)] = 0
```

The following analysis repeats the negativ control analysis, except that an offset is used for each patient to correct for the effect of the index drug. For a single patient, where no index drug is specified, the effect is set to zero. For drugs, where the model could not be fitted, the effect is also set to zero.

```{r}
	f1 = outcomePrimNC ~ AGE + EQ5D + STUDYARMC + Naller + Ncome + COUNTRY + (1|COUNTRY:CENTER);
	rPrimNCcm = glmer(f1, family = binomial(), data = dataNCprim, glmerControl(optimizer = 'bobyqa', boundary.tol = 0, tol = 1e-3, optCtrl = list(maxfun = 1e5)), offset = off);
	print(summary(rPrimNCcm));
```


# Session info

```{r}
	sessionInfo()
```
